```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

'Tis the season to eat, drink, and be merry. In that spirit of merriment, I asked this question: "Can you predict wine quality using just the physical and chemical characteristics of the wine?"

Of course! Using machine learning, anyone can create predictive models to answer just such a question. So During this holiday break, I did just that.  I practiced training linear regression models using `caret` with the goal to predict wine quality using just its intrinsic physical and chemical characteristics.

Grab a glass and review my vignette here: [Training Linear Regression Models using `caret`](https://not-that-john-williams.github.io/regression-wine-quality/)  

```{r eval=FALSE, echo = FALSE}
# code used to generate this blog post
rmarkdown::render("_Rmd/2021-12-20-Training-Linear-Regression-Models-Using-caret.Rmd", 
                  output_format = "github_document", 
                  output_dir = "_posts", 
                  output_file = "2021-12-20-Training-Linear-Regression-Models-Using-caret")
```
