```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### On Ethics

In August 2021, I wrote the blog post “What is a Data Scientist?”  My answer:  statistician + software engineer + artist.  But I left out another key role.  Data scientists also must be respected ethicists, and a quick review of what can go wrong when data scientists are irresponsible shows why.  Personal information is unprotected or published without permission.  Stereotypes are reinforced in predictive policing.  Automated decision-making limits economic opportunities in school admissions, job hiring, and loan approvals.  Healthcare decisions could be made incorrectly, compromising a person’s health and even their life.  And, most recently in the public discourse, democratic systems can be undermined when data scientists use algorithms to sow mistrust and discord on social media.  All of these can be consequences when ethics is not top-of-mind in a data scientist’s training and professional career.  That’s why, after some reflection, I felt obligated to add to my definition of a data scientist--part statistician, part software engineer, part artist, and part ethicist.


### On R,
I’ve used SAS and R during my education at North Carolina State University.  For me, R (and R Markdown specifically) is a much better environment for generating reports, creating ad hoc plots/graphics, and documenting the data science process.  Doing the same in SAS is cumbersome and inefficient—maybe I just don’t know how, but I can never get the SAS output to look like I want.  R lets me be creative.  The numerous open-source packages make R elegantly flexible for whatever data science task I have.  I can access databases and API’s, create predictive models, and design interactive web applications.  I have several personal data science projects that I look forward to completing using R.  Going forward, I’ll be using R Markdown for note taking on data science projects, using Git for version control, and sharing my insights on my GitHub blog.  One thing I hope to create soon is an R Markdown notebook of my frequently “how-to” web searches for R, so I can commit them to long-term memory.  The more I can instantly recall R syntax or R methods versus searching for them will make my programming more efficient.

## Code Used to Generate This Blog Post

```{r eval=FALSE}
rmarkdown::render("_Rmd/2021-11-29-Reflections.Rmd", 
                  output_format = "github_document", 
                  output_dir = "_posts", 
                  output_file = "2021-11-29-Reflections.md")
```


