```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")
```

My first adventure into programming languages was a project in BASIC in 5th grade. I made one pixelated number "bump" on screen into another pixelated number to create its sum. At the time, I thought that was the coolest thing I'd ever gotten to do in school. I didn't jump back into computer programming until college. I took courses in C and C++. Later, in graduate school, I tackled SAS and R. 

## R vs. Other Programming Languages

As someone who thrives on structure, I didn't mind how syntactically strict C, C++, and SAS are. I think that made them easy to master in a short time. R, on the other hand, has lots of flexibility in syntax. This means R code is easily readable, a huge win over other programming languages.  The only downside to this syntactic Wild West is R has a steeper learning curve than other programming languages. R users have to put in the time and effort sailing the seemingly endless ocean of libraries to find--and then learn the unique syntax for--the right one. Do you need previous experience with a programming language to learn R?  No, but I think it would be more difficult to learn without a solid programming background. By learning C and C++ first, I was already comfortable with concepts like object-oriented programming, functions, pointers, loops, and logic. I can imagine how challenging it would be to learn these general programming concepts and navigate R syntax at the same time.

Once you learn R, you can see how functional it truly is. While not a broad, general programming language like C++, R excels at for what it was designed: data science. It was designed by statisticians for statisticians, so it's harder for those outside of data science (like computer engineers) to understand the value R has. They complain that R is "slow" and "lacks scalability". That may be true in some sense, but as open-source software, R is free (unlike its commercial competition SAS) and perfect for collaborating with fellow data scientists. And for someone who's worked with pointers in C++, R is a breath of fresh air--no memory corruption issues! Also, you can create custom operators in R. You can't do that in C++.

Just know learning R never stops. I've been utilizing R for over a year now and I regularly stumble across something new-to-me. A quick view of #rstats tweets reveal that even decade-long R users are continuously innovating, discovering, and sharing new functionality and methodology. R is a language that is still evolving, where every R user contributes to make R a better tool, and where we never stop learning together.

## Example R Markdown Output

```{r}
plot(trees)     # A plot of the dataset "trees"
```

## Code Used to Generate This Blog Post

```{r eval=FALSE}
render("_Rmd/2021-9-13-Programming-Background.Rmd", output_format = "github_document", output_dir = "_posts", output_options = list(html_preview = FALSE))
```
