```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Predictive modeling, a major component of data science, uses statistical techniques to predict future outcomes. Its goal is to answer the question: "Based on known past behavior, what is most likely to happen in the future?" Some real-world applications of predictive modeling are forecasting patterns in weather, predicting performance in sports, anticipating buying behavior in retail, and detecting disease in healthcare. While not foolproof, this method tends to have high accuracy rates, which is why it is commonly used by data scientists.

In this project, we demonstrate a simple predictive analysis:  collecting data, conducting exploratory data analysis, training predictive models, and validating the models performance on test data. We used the `OnlineNewsPopularity` dataset from the [UC Irvine Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/). Click the links below to dive into the analysis:

[Project 2 for ST 558](https://srlmt.github.io/Project-2/)

[Github Repo for Project 2](https://github.com/Srlmt/Project-2)

## Post-Mortem Reflection

### What would you do differently?

I'll answer the opposite of this question: What would I not do differently? I'm glad my partner and I set up communication guidelines and expectations at the very beginning of the project. We agreed that frequent and clear communication in both e-mails, code comments, and commit notes were vital to our success. This collaboration would have been immensely more difficult if we did not communicate as well as we did.

### What was the most difficult part for you?

Within this project, we automated R Markdown to generate 6 reports. Each report was a predictive analysis on a subset of the `OnlineNewsPopularity` dataset. This was my first time attempting automation.  It was where I spent the majority of my time working out the bugs in the code.

### What are your big takeaways from this project?

Version control made collaboration with a partner easy. I had minimal issues with merge conflicts and the small problems I did have were great learning experiences. (Don't forget to "pull" from the repo before beginning your work for the day!)

Ensemble prediction methods can be very powerful. Random Forest and Boosted Tree models quite often outperform Linear Regression models in predictive accuracy.

## Code Used to Generate This Blog Post

```{r eval=FALSE}
rmarkdown::render("_Rmd/2021-10-30-Creating-Predictive-Models-and-Automating-R-Markdown.Rmd", 
                  output_format = "github_document", 
                  output_dir = "_posts", 
                  output_file = "2021-10-30-Creating-Predictive-Models-and-Automating-R-Markdown.md")
```
